---
title: "Module 2 Assignment 1"
author: "Ray"
format: 
  html:
    embed-resources: true
---

## Libraries

```{r}
library(tidyverse)
```

## Assignment
Complete the exercises in chapter 2, section 2.5 of R for Data Science

### Interpretation

In 2–4 sentences, state in plain language why Wickham has you work through these examples in the context of chapter 2, and identify one assumption or limitation of his methodology and why it matters.

## Questions

Q1. Why does this code not work?

```{{r}}
my_variable <- 10
my_varıable # ı is not i
#> Error:
#> ! object 'my_varıable' not found
```

Q2. Look carefully! (This may seem like an exercise in pointlessness, but training your brain to notice even the tiniest difference will pay off when programming.)

Tweak each of the following R commands so that they run correctly:


```{r}
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  geom_smooth(mapping = aes(x = displ, y = hwy), method = "lm")
```

Q3. Press Option + Shift + K / Alt + Shift + K. What happens? How can you get to the same place using the menus?

Keyboard shortcuts (too many!)

Q4. Let’s revisit an exercise from the Section 1.6. Run the following lines of code. Which of the two plots is saved as mpg-plot.png? Why?

```{r}
my_bar_plot <- ggplot(mpg, aes(x = class)) +
  geom_bar()
  
my_scatter_plot <- ggplot(mpg, aes(x = cty, y = hwy)) +
  geom_point()

ggsave(filename = "mpg-plot.png", plot = my_bar_plot)
```
