---
title: "Module02 Assignment03"
author: "Ray Hoobler"
format: 
  html:
    embed-resources: true
---

## Libraries 

```{r}
library(tidyverse)
library(palmerpenguins)
```
## Assignment

Ask a question about the `penguins` data frame and use `dplyr` functions to answer it.

Use the final output of your analysis to create a table and TWO ggplot2 visualizations. For your explanatory visualizations, include a title, subtitle, axis labels, and a caption.

Be sure to review the rubric to ensure you receive full credit for the assignment.


## My question: Is there a strong relationship between bill depth and body mass for each species?

### Visualizations 

```{r}
penguins |> 
  ggplot(aes(bill_depth_mm, body_mass_g, color=species)) +
  geom_point(na.rm = TRUE) +
  geom_smooth(method = "lm", formula = "y ~ x", na.rm = TRUE) +
  labs(
    title = "If we don't group by species, we have an example of \"Simpson\'s Paradox",
    subtitle = "Corresponding tables based on fromulas from Chapter 3 of ISLR",
    caption = "https://allisonhorst.github.io/palmerpenguins/",
    x = "Bill Depth (mm)",
    y = "Body Mass (g)",
    color = "Species"
  ) +
  theme_classic()
```

### Table of slopes 

The formula for calculating the slope of a line using least squares [ISLR, Chapter 3](https://www.statlearning.com)

$$
m = \frac{\sum_{i=1}^{n} (x_i-\bar{x})(y_i-\bar{y})}{\sum_{i=1}^{n} (x_i-\bar{x})^2}
$$

### Create a function for calculating slope

```{r}
slope_nist <- function(x, y) {
  sum((x - mean(x, na.rm = TRUE))*(y - mean(y, na.rm = TRUE)), na.rm = TRUE) / sum((x - mean(x, na.rm = TRUE))^2, na.rm = TRUE)
}
```

Testing function above

```{r}
penguins |> 
  group_by(species) |> 
  summarize(slope = slope_nist(bill_depth_mm, body_mass_g)) |> 
  ungroup()
```

I also want the confidence interval for the slope.

$$
\begin{align}
SE_m = \frac{s}{\sqrt{ \sum{(x - \bar{x})^2}}} \\ \\
\textrm{where:} \qquad   s = \sqrt{ \frac{\sum{(y - \bar{y})^2}}{n-2} }
\end{align}
$$
Repeat the work above to create a function for standard error of the slope.

```{r}
slope_se <- function(x, y) {
  s = sqrt(sum((y - mean(y, na.rm = TRUE))^2, na.rm = TRUE) / (length(y) - 2))

  se_m = s / sqrt(sum((x - mean(x, na.rm = TRUE))^2, na.rm = TRUE))
  
  return(se_m)
}
```

The CI is defined as $t_{0.05/2} \times SE_{slope}$

```{r}
penguins |> 
  group_by(species) |> 
  summarize(
    n = n(),
    slope = slope_nist(bill_depth_mm, body_mass_g),
    ci_95 = slope_se(bill_depth_mm, body_mass_g) * qt(0.975, df = n -2)
    ) |> 
  ungroup()
```

Finally, I can round the slope and ci_95 values. This is a bit messy as we are starting to "nest" functions. For a publication quality table, I'd do this inside of the R package Great Tables (GT); however, this is outside what we can cover in the course.

```{r}
my_table <- penguins |> 
  group_by(species) |> 
  summarize(
    n = n(),
    slope = round(slope_nist(bill_depth_mm, body_mass_g), 1),
    ci_95 = round(slope_se(bill_depth_mm, body_mass_g) * qt(0.975, df = n -2), 1)
    ) |> 
  ungroup()

my_table
```


If my analysis is correct, the slopes are significant; however, the upper and lower confidence values would overlap for all species (barely). 

```{r}
my_table |> 
  ggplot() +
  geom_errorbar(aes(x = species, ymin = slope - ci_95, ymax = slope + ci_95), width = 0.3) +
  geom_point(aes(x = species, y = slope), size = 4) +
  labs(
    title = "\"Statistically\" there is no difference in the relationship \n body_mass_g to bill_depth_mm between species",
    subtitle = "Uncertainty calcuated using formulas from ISLR Chapter 3",
    caption = "https://allisonhorst.github.io/palmerpenguins/",
    x = "Species",
    y = "Slope +/- 95% Confidence Intervals"
  )
```


