---
title: "Module04 Assignment02"
author: "Ray James Hoobler"
format: 
  html:
    embed-resources: true
df-print: paged
---

## Libraries

```{r}
library(tidyverse)
```


## Furnace dataset

### Info from the file

Number of observations                       = 168
Number of observations per line image        = 4
Order of variables on a line image--
   1. Factor Variable RUN          = Run Number
   2. Factor Variable ZONE         = Each furnace has 4 "zones"
   3. Factor Variable WAFER        = Within each zone, 2 wafers are
                                     measured
   4. Dependent Variable THICKNESS = Film Thickness (Angstroms)
  
To read this file into Dataplot--
   SKIP 25
   READ FURNACE.DAT RUN ZONE WAFER THICKNESS


RUN   ZONE    WAFER    THICKNESS

## From the case study's description

>The goal of this study is to determine if this process is capable of consistently growing oxide films with a thickness of 560 Angstroms +/- 100 Angstroms. An additional goal is to determine important sources of variation for use in the development of a process control strategy.

### NOTE

The factor variable WAFER is not accurate as the two wafers in each zone are unique for every run. **The only comparison we can make is between wafers 1 and 2 in a given zone for a given run.**

```{r}

column_names_furnace <- str_split_1("RUN   ZONE    WAFER    THICKNESS", pattern = "\\s+") |> str_to_lower()
column_names_furnace

furnace <- read_table("data/FURNACE.DAT", 
                      skip = 25, 
                      col_names = column_names_furnace,
                      col_types = "iffd"
                      )

furnace
```

## EDA of FURNACE.DAT

### Summary statistics (base R)

```{r}
furnace |>
  select(thickness) |> 
  summary()
```

### Summary statistics (`group_by()` and `summarise`)


```{r}
furnace |> 
  summarise(
    .by = zone, 
    mean_zone = mean(thickness, na.rm = TRUE),
    sd_zone = sd(thickness, na.rm = TRUE)
    )
```


### Run sequence plot

```{r}
furnace |> 
  ggplot(aes(seq_along(thickness), thickness)) +
  geom_line() +
  geom_hline(yintercept = 560, color = "black", linetype = "dashed") +
  geom_hline(yintercept = c(560 + 100, 560 - 100), color = "red", linetype = "dashed") +
  geom_smooth(method = "lm", formula = "y ~ x") +
  labs(
    title = "Run sequence plot show small drift over time"
  )
```

### Scatter plot of thickness by run

```{r}
furnace |> 
  ggplot(aes(run, thickness)) +
  geom_point(alpha = 1/2)
```


### Box and whiskers plot to comnpare zones

```{r}
furnace |> 
  ggplot(aes(zone, thickness)) +
  geom_boxplot(notch = TRUE) +
  labs(
    title = "Box and whiskers plot implies no significant difference between zones"
  )
```

### Does the data reasonably follow a normal distribution

```{r}
furnace |> 
  ggplot() +
  geom_histogram(aes(x = thickness), bins = 50)
```


```{r}
furnace |> 
  ggplot() +
  geom_qq(aes(sample = thickness)) +
  geom_qq_line(aes(sample = thickness), color = "red")
```

### Are there trends **within** the data?

```{r}
furnace_2 <- furnace |> 
  rownames_to_column() |> 
  mutate(week = case_when(
    run <= 7 ~ "week 01",
    run > 7 & run <= 14 ~ "week 02",
    run  > 14 ~ "week 03"
  )
)

furnace_2
```


```{r}
furnace_2 |> 
  ggplot(aes(run, thickness, color = week)) +
  geom_point() +
  geom_smooth(method = "lm", formula = "y ~ x") +
  labs(
    title = "Further reduction of the PM cycle may improve performance"
  )
```



